%-------------------------
% Resume in LateX
% Author : Ahmed Charfeddine
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Ahmed Charfeddine}} & Email: \href{mailto:ahmed.charfeddine216@gmail.com}{ahmed.charfeddine216@gmail.com}\\
  Full-Stack Developer | Web \& Mobile& Mobile: \href{tel:+21654946860}{+216-54-946-860} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ESPRIT - Private Higher School of Engineering and Technology}{Ariana, Tunisia}
      {Master’s Degree in Information Technology}{Sep 2019 -- Nov 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SQLI Services }{Manouba, Tunisia}
      {Full-Stack Web and Mobile Developer}{Apr 2025 -- Present}
\begin{itemize}
\item Developed a mobile application using Firebase and Java to support users interested in Mediterranean dieting and fitness with healthy habit courses and interactive challenges
\item Built an interactive game module to evaluate users' understanding of the Mediterranean diet with instant feedback and performance analysis
\item Implemented a fitness and diet chatbot that provides personalized guidance, analyzes food images for calories and ingredients, and checks recipe healthiness
\item Constructed an Instagram-style community for dieting and fitness, enabling users to share recipes, follow others, comment, react, and chat with friends
\end{itemize}
      
% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 -- Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd

%-------------------------------------------

    \resumeSubheading
      {I-Lead Consulting}{Charguia, Tunisia}
      {Full-Stack Developer}{Feb 2024 -- July 2024}
\begin{itemize}
\item Implemented a code editor for a candidate skill-testing platform using Spring Boot and Angular with 13 multi-language compiler integration
\item Created sample test cases and expected outputs for automated evaluation of submitted solutions using Docker for containerization
\item Ensured scalability and consistent environment setup across different programming language assessments
\end{itemize}

    \resumeSubheading
      {ESPRIT}{Ariana, Tunisia}
      {Mobile Developer}{June 2023 -- Aug 2023}
 \begin{itemize}
\item Developed a medical mobile application using Kotlin and Firebase for predicting venous thrombosis probability based on user medical data
\item Integrated data analysis algorithms and secure data handling for medical risk assessment
\end{itemize}

  \resumeSubHeadingListEnd


%-----------Technical Skills-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}
      {Java, Kotlin, JavaScript, TypeScript, PHP, HTML/CSS.}
    \resumeSubItem{Frameworks \& Libraries}
      {Spring Boot, Angular, Symfony, React, QT.}
    \resumeSubItem{Databases}
      {MySQL, PostgreSQL, MongoDB, Firebase, H2, NoSQL.}
    \resumeSubItem{Tools \& Technologies}
      {Github, Docker, Gitlab, Google Cloud, Postman, REST APIs, Agile Methodology.}
  \resumeSubHeadingListEnd


% --------CERTIFICATIONS------------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{Saylor Academy}
      {ESL005: Business-Proficient English as a Second Language.}
    \resumeSubItem{Coursera}
      {Messenger ChatBot Certificate.}
    \resumeSubItem{Bourguiba School of Languages (2014 - 2018)}
      {Japanese Language Program.}
    \resumeSubItem{Sololearn}
      {JavaScript Certification.}
  \resumeSubHeadingListEnd


  % --------LANGUAGES------------
\section{Languages}

  \resumeSubHeadingListStart
    \resumeSubItem{Tunisian}
      {Native.}
    \resumeSubItem{French}
      {Fluent.}
    \resumeSubItem{Arabic}
      {Fluent.}
    \resumeSubItem{English}
      {Fluent.}
    \resumeSubItem{Japanese}
      {Basic - 4 years of language training.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
